Microbial interactions as drivers of a chemostat ecosystem

### 2020-01-09 tex/Tracking.tex
Last changes, version sent for internal revision.

\title{Interactions in a chemostat as the driver of an ecosystem.}
%% \title{Correcting/Improving chemostat models from microbial interactions}
%% Including microbial ecology in a chemostat model: tracking microbial interactions
%% 
%% Extending a chemostat model 
%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{<author name>}
%% \address[label1]{<address>}
%% \address[label2]{<address>}

@@

\begin{abstract}
	This article deals with the inclusion of microbial ecology advances in bioprocess modelling. The first part presents the mathematical analysis of a model that may be framed within the class of Lotka-Volterra models fitted to experimental data in a chemostat setting. The limitations and the insights of such an approach are discussed. The main novelty of this work lies in the second part, where the use of an optimal tracking technique for the integration of genetic sequencing in chemostat models is presented. The method revisits the data used for the first model presented. 
\end{abstract}

@@

The contribution of this article is a new method to integrate the microbial community measurements in chemostat models, based on any sequencing technique that can quantify the species abundances through time. This is a first step towards developing predictive models of a reactor's performance based on the microbial community structure.

@@

In section 5 the methodology from section 4 is applied to all of the data from the experiments performed by Dumont \textit{et al}\cite{Dumont2009} and not just to the most abundant species as it was the case of the model analysed in section 2\cite{Dumont2016}. The article ends with a discussion on the scope of applicability of the method and further development.

@@

Notations used throughout the article are:
\begin{enumerate}
	\item $n$: the number of OTU considered.
	\item $n_i, \, i \in \{1,2\}$: the number of OTU in functional group $G_i$.
	\item Let $m$ be an interger then $[m]:=\{1,\dots,n \}$. 
	\item $x_i$ :  is the concentration of OTU $i$ measured in $[g/l]$. $i \in [n]$. 
	\item $x$: vector $(x_1,\dots,x_n)^\top$.
	\item $s_1$ : concentration of substrate 1 in $[g/l]$.
	\item $s_2$ : concentration of substrate 2 in $[g/l]$. 
	\item $s_3$ : concentration of substrate 3 in $[g/l]$.
	\item $s$:  vector $(s_1,s_2,s_3)$. Refered to as metabolites, or chemical species.
	\item $\I_i(t,x)$ : Interaction function of OTU $i \in \{1,\dots,n\}$.
	\item $\mu_i(s,x)$ : growth function of OTU $i \in \{1,\dots,n\}$.
	\item $\mu = (\mu_1(s,x), \dots, \mu_n(s,x))$ vector containing the growth function of every OTU.
	\item $D$: Dilution Rate of the continuous reactor in $[1/day]$. 
	\item $y_i$: Yield of moles of biomass formed per mole of substrate consumed of OTU $i$.
	\item $y$: vector $y_1,\dots,y_n$.
	\item $k_i$: Yield of  moles of substrate consumed per mole of biomass formed of OTU $i$ . The inverse of the biomass yield $k_i = \dfrac{1}{y_i}$.
	\item $k$: vector $k_1,\dots,k_n$.
	\item For integers $m_1$ and $m_2$ and $a \in \R$, $a_{m_1 \times m_2}$ represents a matrix of $m_1$ rows and $m_2$ columns with $a$ in every entry. 
	\item Let $m$ be an integer then $I_m$ is the identity matrix of size $m$.
\end{enumerate}

@@

Observe that equilibrium points are by definition non-negative so the state variables can have biological meaning. Details of the calculations are given in the appendix.

@@

\begin{defn} Given a vector $v=(v_1,\dots, v_n)\in \R^n$, the function $\diag(v)$ stands for:
	\begin{align}
	\begin{array}{rc}
	\diag:\R^n \rightarrow & \mathbb{M}_{n\times n}(\R)\\
	& \\
	v \rightarrow & \begin{pmatrix}
	v_1 & 0 & \dots & 0 \\
	0 & v_2 & \ddots & \vdots\\ 
	\vdots & \ddots & \ddots& 0 \\
	0 & \dots &0 & v_n 
	\end{pmatrix}
	\end{array}
	\end{align}
\end{defn}

The former function places a vector $v$ in the diagonal of a matrix. Recalling $A$ the matrix with coefficients $a_{ij}$. The following notation is introduced.

@@

Formulae for coefficients $c_1, c_2, c_3, a_0, a_1, a_2, a_3, a_4$ can be found in the appendix.

@@

\subsection{Local Stability and Operating Diagrams}
For checking local asymptotic stability of the equilibria points, the Jacobian of the system is provided and evaluated at each of these points. The resulting matrix's eigenvalues must have negative real part. A general formula for this Jacobian is presented in the appendix.

@@

The operating diagram from one of the sets of the parameter identification from Dumont et al. is presented in figure \ref{OD Dumont} from a Bayesian estimation method. Two species per functional group were considered. One can see that coexistence in the same functional group is never attained. However when using a different set of parameters one can see a more complex situation where coexistence in the same functional group is possible as seen in figure \ref{OD modified}. In the latter case CN can be achieved at a more elevated dilution rats than in the former case. Parameters of cases 1 and 2 can be seen in table \ref{Parameters Dumont} and \ref{Parameters Modified}, respectively.

@@

\begin{table}[ht]
	\centering
	\begin{tabular}{|l|l|l|l|}
		\hline
		Modified Parameters  & $\mu_i\,[1/day]$ & $K_i\,[mg/L]$ & $\frac{1}{y_i} \, [gr/gr]$ \\ \hline
		$x_1 \in G_1$ &0.828  &0.147  & 5 \\ \hline
		$x_2\in G_1$ & 0.621 & 0.0147 & 3 \\ \hline
		$x_3\in G_2$ & 0.18 & 0.026 & 110 \\ \hline
		$x_4\in G_2$ & 0.135& 0.0026& 90 \\ \hline
	\end{tabular}
	\caption{Kinetic parameters of model \eqref{system} modified from \cite{Dumont2016}.}
	\label{Parameters Modified}
\end{table}
\begin{figure}[ht]
	\centering	
	\begin{subfigure}[b]{0.45\textwidth}
		\includegraphics[width=\textwidth]{Interactions_Parameters_modifed}
	\end{subfigure}
	\begin{subfigure}[b]{0.45\textwidth}
		\includegraphics[width=\textwidth]{OD_parameters_modified}
	\end{subfigure}
	\caption{Left: interactions of the system. Right: operating diagram of Model \eqref{system}, with parameters in Table \ref{Parameters Modified}. The different zones represent the surviving species in the steady state. PN takes place when neither $x_3$ nor $x_4$ are present. CN takes place if $x_3$ or $x_4$ are present.}
	\label{OD modified}
\end{figure}
\clearpage

@@

The model here presented serves to illustrate that by considering a more complex growth rate that tries to model ecological interactions one might explain differences in reactors operating under similar conditions. It also shows a new mechanism by which the CEP no longer holds. The operating diagrams always show a single stable equilibrium point for each pair $(s_{in},D)$, however no proof is offered to such conjecture.

@@

For the reader to gain understanding of the situation, a simulation of the system using the experiments operating parameters ($D$ and $s_{in}$) is presented without control (i.e. $u(t)= 1$) in  Figure \ref{u=1_metabolites}. $s_3$ accumulates all along the trajectory, but when compared to data it is clear that $s_3$ stops accumulating after a while. The community dynamics is neither captured by this simulation as seen in figures \ref{u=1_AOB} and \ref{u=1_NOB}.

@@

\begin{figure}[h]
	\centering
	\includegraphics[width= 0.4\textwidth]{Application//191218_Reactor_A_NOB_Iter_0}
	\caption{Simulation when $u=1$. }
	\label{u=1_NOB}
\end{figure}

When applying the presented method one obtains the simulation that can be seen in figure \ref{ControlSimulation}. The method captures the tendencies in the measured substrates, but not their absolute values. The simulation of each functional $G_1$ (AOB), and $G_2$ (NOB) can be seen in figures \ref{AOBSimulation} and \ref{NOB Simulation}, respectively. Note that the fit of $G_1$ seems better than the fit of $G_2$, which can be explained by the 1 order of magnitude difference of abundance between the members of the group.

@@

The tracking model was proposed  in a chemostat setting as a way to correct a substrate limited expression. However the technique could be used in contexts where less information on the growth function of microbes is known. If one supposes nothing on the growth expression but the fact that is bounded (life cannot grow infinitely fast) the model actually becomes a linear model and one recovers a classic quadratic regulator for linear systems. Nevertheless, even in the former case, the synthesis of the optimal bounded control remains an open theoretical challenge.

The interaction function introduced tries to address the issue of prediction from the genetic sequencing. The analysis of the gLV model proposed by \cite{Dumont2016}.   From the application section one can retain the hypothesis that linear pairwise interaction model do not capture the complexity of the particular nitrifying chemostat analysed.  This opens the question for a broader class of interaction functions that could fit well complex microbial ecosystems. The experimental study in chemostat systems seems a good compromise between completely open ecosystems (nature) and controlled conditions (laboratory) in order to explore expressions that could account for microbial interactions.
It is not then possible to reconstruct the original interaction matrix in the current form of the optimal control problem, thus suggesting to take the derivative of the control in the cost function, instead of the control itself.

@@

Discussion on how to use the method for calibration.

@@

All the codes can be recovered from the following repository \url{https://github.com/paus-5/Class-and-Track}.
\section{Acknowledgements}
 The authors would like to thank Alain Rapaport for the fruitful exchanges. This work was financed by grant Thermomic. And a sejour

\section{Appendix}

@@

Recall $A_{11} = \diag \left( f\left(s^{[i-1]}\right)- D_{n\times 1} \right)$, and $B_1 = \diag\left(f\left(s^{[i-1]}\right)\right)\diag \left(x^{[i-1]} \right) $ The equations for $\tilde{P}^{[i]}(t)$:
\begin{align}
\dot{\tilde{P}}^{[i]}(t)= -Q- \tilde{P}^{[i]}A_{11} -A_{11}^\top \tilde{P}^{[i]} + \dfrac{1}{\lambda} \tilde{P}^{[i]}B_1B_1^\top \tilde{P}^{[i]} \\
\tilde{P}^{[i]}(t_f) = 0
\end{align}

Inspecting the former equation one notices that if $i\neq j$, $P_{ij}(t) = 0$ is a solution of all non diagonal entries. And therefore by existence and uniqueness they should be constantly zero. Hence only the diagonal entries should be calculated. 
\begin{align}
\dot{\tilde{P}}^{[i]}_{jj}(t)= -Q_{jj}- 2 \left(f_j\left(s^{[i-1]}\right)- D \right)\tilde{P}^{[i]}_{jj} + \dfrac{1}{\lambda}\left(\tilde{P}^{[i]}_{jj}\right)^2f_j\left(s^{[i-1]}\right)^2\left(x^{[i-1]}_j\right)^2  \\
\tilde{P}^{[i]}_{jj}(t_f) = 0
\end{align}

@@

\begin{align}
\dot{\tilde{s}}_f^{[i]}(t) &= -z(t)- \left[A_{11} -\frac{1}{\lambda}B_1B_1^\top \tilde{P}^{[i]}(t) \right]^\top \tilde{s}_f^{[i]} \\
\tilde{s}_f^{[i]}(t_f) &= 0
\end{align}

And the control law is given by
\begin{align}
v^{[i]}(t)_j = \max \left\{ -1,\min\left\{0,\left( -\dfrac{1}{\lambda}B_1^\top\left(X^{[i-1]}(t)\right)\left(\tilde{P}^{[i]}(t)x^{[i]}(t)-\tilde{s}_f^{[i]}(t)\right)\right)_j \right\}\right\} \forall j \in [n]
\end{align}

They were solved using standard backward numerical integration.

>>>>

\title{Microbial interactions as drivers of a chemostat ecosystem}
%% \title{Correcting/Improving chemostat models from microbial interactions}
%% Including microbial ecology in a chemostat model: tracking microbial interactions
%% 
%% Extending a chemostat model 
%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{<author name>}
%% \address[label1]{<address>}
%% \address[label2]{<address>}

@@

\begin{abstract}
	This article deals with the inclusion of microbial ecology advances in bioprocess modelling. The first part presents the mathematical analysis of a model that may be framed within the class of Lotka-Volterra models fitted to experimental data in a chemostat setting. The limitations and the insights of such an approach are discussed. The main novelty of this work lies in the second part, where the use of an optimal tracking technique for the integration of genetic sequencing in chemostat models is presented. The method revisits the experimental data used for the first model. 
\end{abstract}

@@

The contribution of this article is a new method to integrate the microbial community measurements in chemostat models, based on any sequencing technique that can quantify the species abundances through time. This is a first step towards developing predictive models of a reactor's outcome based on the microbial community structure.

@@

In section 5 the methodology from section 4 is applied to all of the data from the experiments performed by Dumont \textit{et al}\cite{Dumont2009} and not just to the most abundant species as it was the case of the model analysed in section 2\cite{Dumont2016}. The method shows that by following the community dynamics one can reconstruct the dynamics of the chemical species. The article ends with a discussion on the scope of applicability of the method and perspectives.

@@

Notations used throughout the article:
\begin{enumerate}
	\item $n$: the number of OTU considered.
	\item $n_i, \, i \in \{1,2\}$: the number of OTU in functional group $G_i$.
	\item Let $m$ be an interger then $[m]:=\{1,\dots,n \}$. 
	\item $x_i$ :  is the concentration of OTU $i$ measured in $[g/l]$. $i \in [n]$. 
	\item $x$: vector $(x_1,\dots,x_n)^\top$.
	\item $s_1$ : concentration of substrate 1 in $[g/l]$.
	\item $s_2$ : concentration of substrate 2 in $[g/l]$. 
	\item $s_3$ : concentration of substrate 3 in $[g/l]$.
	\item $s$:  vector $(s_1,s_2,s_3)$. Refered to as metabolites, or chemical species.
	\item $\I_i(t,x)$ : Interaction function of OTU $i \in \{1,\dots,n\}$.
	\item $\mu_i(s,x)$ : growth function of OTU $i \in \{1,\dots,n\}$.
	\item $\mu = (\mu_1(s,x), \dots, \mu_n(s,x))$ vector containing the growth function of every OTU.
	\item $D$: dilution rate of the continuous reactor in $[1/day]$. 
	\item $y_i$: yield of moles of biomass formed per mole of substrate consumed of OTU $i$.
	\item $y$: vector $y_1,\dots,y_n$.
	\item $k_i$: yield of  moles of substrate consumed per mole of biomass formed of OTU $i$ . The inverse of the biomass yield $k_i = \dfrac{1}{y_i}$.
	\item $k$: vector $k_1,\dots,k_n$.
	\item For integers $m_1$ and $m_2$ and $a \in \R$, $a_{m_1 \times m_2}$ represents a matrix of $m_1$ rows and $m_2$ columns with $a$ in every entry. 
	\item Let $m$ be an integer then $I_m$ is the identity matrix of size $m$.
\end{enumerate}

@@

Observe that equilibrium points are by definition non-negative so the state variables can have physical meaning. Details of the calculations are given in the appendix.

@@

\begin{defn} Given a vector $v=(v_1,\dots, v_n)\in \R^n$, the function $\diag(v)$ stands for:
	\begin{align}
	\begin{array}{rc}
	\diag:\R^n \rightarrow & \mathbb{M}_{n\times n}(\R)\\
	& \\
	v \rightarrow & \begin{pmatrix}
	v_1 & 0 & \dots & 0 \\
	0 & v_2 & \ddots & \vdots\\ 
	\vdots & \ddots & \ddots& 0 \\
	0 & \dots &0 & v_n 
	\end{pmatrix}
	\end{array} \label{diag_operator}
	\end{align}
\end{defn}

Function \eqref{diag_operator} places a vector $v$ in the diagonal of a matrix. Recalling $A$ the matrix with coefficients $a_{ij}$. The following notation is introduced.

@@

Formulae for coefficients $c_1, c_2, c_3, a_0, a_1, a_2, a_3, a_4$ can be found in supplementary material.

@@

\subsection{Local Stability and Operating Diagrams}
For checking local asymptotic stability of the equilibria points, the Jacobian of the system is provided and evaluated at each of these points. The resulting matrix's eigenvalues must have negative real part. A general formula for this Jacobian is presented in the supplementary material.

@@

The operating diagram from one of the sets of the parameter identification (obtained with a Bayesian estimation method) from Dumont et al. is presented in figure \ref{OD Dumont}. Their fit describes well the dynamics of the OTU, which is not the case for measured chemical species. Two OTU per functional group were considered. One can see that coexistence in the same functional group is never attained. However when using a different set of parameters one can see a more complex situation where coexistence in the same functional group is possible as seen in figure \ref{OD modified}. In the latter case CN can be achieved at a more elevated dilution rats than in the former case. Parameters of cases 1 and 2 can be seen in table \ref{Parameters Dumont} and \ref{Parameters Modified}, respectively.

@@

\begin{table}[ht]
	\centering
	\begin{tabular}{|l|l|l|l|}
		\hline
		Modified Parameters  & $\mu_i\,[1/day]$ & $K_i\,[mg/L]$ & $\frac{1}{y_i} \, [gr/gr]$ \\ \hline
		$x_1 \in G_1$ &0.828  &0.147  & 5 \\ \hline
		$x_2\in G_1$ & 0.621 & 0.0147 & 3 \\ \hline
		$x_3\in G_2$ & 0.18 & 0.026 & 110 \\ \hline
		$x_4\in G_2$ & 0.135& 0.0026& 90 \\ \hline
	\end{tabular}
	\caption{Kinetic parameters of model \eqref{system} modified from \cite{Dumont2016}.}
	\label{Parameters Modified}
\end{table}
\begin{figure}[ht]
	\centering	
	\begin{subfigure}[b]{0.45\textwidth}
		\includegraphics[width=\textwidth]{Interactions_Parameters_modifed}
	\end{subfigure}
	\begin{subfigure}[b]{0.45\textwidth}
		\includegraphics[width=\textwidth]{OD_parameters_modified}
	\end{subfigure}
	\caption{Left: interactions of the system. Right: operating diagram of Model \eqref{system}, with parameters in Table \ref{Parameters Modified}. The 8 different zones represent the surviving species in the steady state. PN takes place when neither $x_3$ nor $x_4$ are present. CN takes place if $x_3$ or $x_4$ are present.}
	\label{OD modified}
\end{figure}
\clearpage

@@

The model here presented serves to illustrate that by considering a more complex growth rate that tries to model ecological interactions one might explain differences in reactors operating under similar conditions. It also shows a new mechanism by which the CEP no longer holds. The operating diagrams always show a single stable equilibrium point for each pair $(s_{in},D)$, however no proof is offered to such conjecture. Since the gLV model discussed (and calibrated in \cite{Dumont2016}) fails to completely capture the dynamics observed in the chemostat experiments,

@@

For the reader to gain understanding of the situation, a simulation of the system using the experiments operating parameters ($D$ and $s_{in}$) is presented without control (i.e. $u(t)= 1$) in  Figure \ref{u=1_metabolites}. $s_3$ accumulates all along the trajectory, but when compared to data it is clear that $s_3$ stops accumulating after a while. The community dynamics is neither captured by this simulation as seen in figure \ref{u=1_NOB} where the NOB community is shown.

@@

\begin{figure}[h]
	\centering
	\includegraphics[width= 0.4\textwidth]{Application//191218_Reactor_A_NOB_Iter_0}
	\caption{Simulation when $u=1$. }
	\label{u=1_NOB}
\end{figure}
\pagebreak
When applying the presented method one obtains the simulation that can be seen in figure \ref{ControlSimulation}. The method captures the tendencies in the measured substrates. The simulation of each functional $G_1$ (AOB), and $G_2$ (NOB) can be seen in figures \ref{AOBSimulation} and \ref{NOB Simulation}, respectively. Note that the fit of $G_1$ seems better than the fit of $G_2$, which can be explained by the 1 order of magnitude difference of abundance between the members of the group.

@@

The tracking model was proposed  in a chemostat setting as a way to correct a substrate limited expression. However the technique could be used in contexts where less information on the growth function of microbes is known. If one supposes nothing on the growth expression but the fact that is bounded (life cannot grow infinitely fast) the model becomes a linear model and one recovers a classic quadratic regulator for linear systems. Nevertheless, even in the former case, the synthesis of the optimal bounded control remains an open theoretical challenge.

The interaction function introduced tries to address the issue of prediction from genetic sequencing. The analysis of the gLV model proposed by Dumont \textit{et al.} \cite{Dumont2016} shows a new mechanism by which the CEP may not hold, however we conjecture that the system seems to have only one positive stable equilibrium. From the application section one can see that by correcting the growth rate one is able to recuperate the chemical species dynamics, implying that interactions are driving the system. The former correction varies strongly and when compared to the proof of section one may hypothesise that linear pairwise interaction model can not capture the complexity of the particular chemostat analysed. This opens the question for a broader class of interaction functions that could fit well complex microbial ecosystems. The experimental study in chemostat systems seems a good compromise between completely open ecosystems (nature) and controlled conditions (laboratory) in order to explore expressions that could account for microbial interactions.

@@

One of the next steps in this line of research would be to synthesize a control that is able to reconstruct interactions functions, and not just the dynamics of the species as is the case presented. One might bypass the end point issue of the current control scheme, by, for example, taking the derivative of the control in the cost function, instead of the control itself, or alternatively by eliminating the control cost and making a very thorough use of the pontryagin maximum principle and the switch function for the synthesis of the controls.

@@

All the codes can be recovered from the following repository \url{https://github.com/paus-5/Class-and-Track}.
\section{Acknowledgements}
 The authors would like to thank Alain Rapaport for the fruitful exchanges. This work was financed by project Thermomic ANR-16-CE04-0003.

\section{Supplementary Material}

@@

Recall $A_{11} = \diag \left( f\left(s^{[i-1]}\right)- D_{n\times 1} \right)$, and $B_1 = \diag\left(f\left(s^{[i-1]}\right)\right)\diag \left(x^{[i-1]} \right) $ The equations for $\tilde{P}^{[i]}(t)$:
\begin{align}
\dot{\tilde{P}}^{[i]}(t)= -Q- \tilde{P}^{[i]}A_{11} -A_{11}^\top \tilde{P}^{[i]} +  \tilde{P}^{[i]}B_1R^{-1}B_1^\top \tilde{P}^{[i]} \\
\tilde{P}^{[i]}(t_f) = 0
\end{align}

Inspecting the former equation one notices that if $i\neq j$, $P_{ij}(t) = 0$ is a solution of all non diagonal entries when $R$ is diagonal. And therefore by existence and uniqueness they should be constantly zero. Hence only the diagonal entries should be calculated. 
\begin{align}
\dot{\tilde{P}}^{[i]}_{jj}(t)= -Q_{jj}- 2 \left(f_j\left(s^{[i-1]}\right)- D \right)\tilde{P}^{[i]}_{jj} + R^{-1}\left(\tilde{P}^{[i]}_{jj}\right)^2f_j\left(s^{[i-1]}\right)^2\left(x^{[i-1]}_j\right)^2  \\
\tilde{P}^{[i]}_{jj}(t_f) = 0
\end{align}

@@

\begin{align}
\dot{\tilde{s}}_f^{[i]}(t) &= -z(t)- \left[A_{11} -R^{-1}B_1B_1^\top \tilde{P}^{[i]}(t) \right]^\top \tilde{s}_f^{[i]} \\
\tilde{s}_f^{[i]}(t_f) &= 0
\end{align}

And the control law is given by
\begin{align}
v^{[i]}(t)_j = \max \left\{ -1,\min\left\{0,\left( -R^{-1}B_1^\top\left(X^{[i-1]}(t)\right)\left(\tilde{P}^{[i]}(t)x^{[i]}(t)-\tilde{s}_f^{[i]}(t)\right)\right)_j \right\}\right\} \forall j \in [n]
\end{align}

They were solved using standard backward numerical integration.
\subsection{Simulations proof of concept}
\textbf{$\lambda = 10^{-1}$}
\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-1//191210_no_noise_Biomass_iter_10}
	\caption{Total biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
	\label{Total Biomass no noise e1}
\end{figure}
\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-1//191210_no_noise_AOB_iter_10_plot_1}
	\caption{AOB biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
	\label{AOB no noise e1}
\end{figure}
\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-1//191210_no_noise_NOB_iter_10_plot_1}
	\caption{NOB biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
	\label{NOB no noise e1}
\end{figure}
\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-1//191210_no_noise_metabolites_iter_10}
	\caption{Metabolites. Dotted line: simulated data. Continuous line: the tracking procedure results.}
	\label{Metabolites no noise e1}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-1//191210_no_noise_Control_AOB_iter_10_plot_1}
	\caption{Control for the AOB population.}
	\label{Control AOB no noise e1}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-1//191210_no_noise_Control_NOB_iter_10_plot_1}
	\caption{Control for the NOB population.}
	\label{Control NOB no noise e1}
\end{figure}
\clearpage
\textbf{$\lambda = 10^{-2}$}
\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-2//191210_no_noise_2_Biomass_iter_10}
	\caption{Total biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
	\label{Total Biomass no noise e2}
\end{figure}
\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-2//191210_no_noise_2_Control_AOB_iter_10_plot_1}
	\caption{AOB biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
	\label{AOB no noise e2}
\end{figure}
\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-2//191210_no_noise_2_Control_NOB_iter_10_plot_1}
	\caption{NOB biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
	\label{NOB no noise e2}
\end{figure}
\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-2//191210_no_noise_2_metabolites_iter_10}
	\caption{Metabolites. Dotted line: simulated data. Continuous line: the tracking procedure results.}
	\label{Metabolites no noise e2}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-2//191210_no_noise_2_AOB_iter_10_plot_1}
	\caption{Control for the AOB population.}
	\label{Control AOB no noise e2}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-2//191210_no_noise_2_NOB_iter_10_plot_1}
	\caption{Control for the NOB population.}
	\label{Control NOB no noise e2}
\end{figure}

\clearpage
